DSCI 445 - Algal Blooms

### 2020-12-10 paper.Rmd
Added how we got the data

TODO:
How we got the data

>>>>

The data came from two sources; satellite data and in situ data from public
sources. The satellite data was downloaded utilizing Google Earth Engine, which
downloaded the data for individual lakes, ignoring images that were over a
threshold of cloud cover. This threshold was because cloud cover would darken
the pixels, skewing the data. The satellite data included all of Landsat 5, 7,
and 8 from the past 35 year and has the different band (wavelength) data for the
center most pixel of each lake. The in situ data includes all public data that
is available for chlorophyll in Colorado. This includes data from sources like
Denver Water, the USGS, and Northern Water. The data that is being utilized is
chlorophyll values, and the data also includes secchi depth (how deep you can
see into the water).
